Understanding both enhanced and impaired learning with enhanced plasticity: a saturation hypothesis (supplementary material)

### 2014-02-18 MHCpaper/MHCsupp.tex
improved plasticity video

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
\documentclass[12pt]{article}
%\usepackage[printfigures]{figcaps}
%\usepackage[nolists,nomarkers]{endfloat}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
\hypersetup{colorlinks,linkcolor=blue,citecolor=teal,urlcolor=teal}
\input{sl_graphics_preamble.tex}
\graphicspath{{"Figures/"}}
%
\usepackage{array}
\newcounter{tablerow}[table]
\newcommand{\tablerowautorefname}{row}
\newenvironment{tabularn}[1]{\begin{tabular}{#1>{\refstepcounter{tablerow}}l}}{\end{tabular}}
%\usepackage{etoolbox}
%\AtBeginEnvironment{tabular}{\setcounter{tablerow}{0}}
\renewcommand{\figureautorefname}{Supplementary Figure}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\I}{\mathbf{I}}
%vec of ones
%equilibrium distribution
\newcommand{\pr}{\mathbf{p}}
\newcommand{\eq}{\pr^\infty}
%other symbols
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\frg}{\W^\mathrm{F}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\F}{\boldsymbol{\Phi}}
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
\newcommand{\norm}{_0}
\newcommand{\inc}{_{\text{inc}}}
\newcommand{\dec}{_{\text{dec}}}
\newcommand{\incdec}{_{\text{inc/dec}}}
\newcommand{\wt}{_{\text{WT}}}
%\newcommand{\ko}{_{\text{D$^\mathrm{b}$K$^\mathrm{b}$-/-}}}
\newcommand{\KO}{D$^\mathrm{b}$K$^{\mathrm{b}-/-}$}
\newcommand{\ko}{_{\text{MHC}}}
%\newcommand{\KO}{MHC}
\newcommand{\tpre}{t_{\text{pre}}}
\newcommand{\ttrain}{t_{\text{train}}}
\newcommand{\lmax}{_{\text{max}}}
\newcommand{\lmin}{_{\text{min}}}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{Understanding both enhanced and impaired learning with enhanced plasticity: a saturation hypothesis (supplementary material)}
%
%% Author List:
%%
%\author{An Author$^a$, Another Author$^b$ and Yet Another Author$^c$\\
%%
%\small{\emph{$^a$ Address 1}}\\
%\small{\emph{$^b$ Address 2}}\\
%\small{\emph{$^c$ Address 3}}\\
%}
\date{}
\DeclareCaptionLabelFormat{supp}{\textbf{#1 S#2}}
\captionsetup{labelformat=supp}

@@

\setcounter{page}{6}
\setcounter{figure}{5}
\maketitle

@@

\begin{figure}[p]
 \begin{center}
 \parbox{0.8\linewidth}{%
 \begin{myenuma}
  \item\aligntop{\includegraphics[height=1.7cm]{serial.svg}}\label{fig:serial_model}\hspace{0.5cm}
  \item\aligntop{\includegraphics[height=1.7cm]{binary.svg}}\label{fig:binary_model}\hspace{0.5cm}\\[1cm]
  \item\aligntop{\includegraphics[height=1.7cm]{multistate.svg}}\label{fig:multistate_model}\hspace{0.5cm}
  \item\aligntop{\includegraphics[height=2.5cm]{cascade.svg}}\label{fig:cascade_model}
 \end{myenuma}
 }
 \end{center}
  \caption[Transition probabilities for different models]{Transition probabilities for different models.
  Potentiation induces transitions indicated by orange arrows, depression indicated by blue arrows.
  States of strong/weak synaptic weight indicated by orange/blue circles.
  (\ref{fig:serial_model}) In the serial model the transition probabilities for potentiation/depression are all equal and it is parameterised by these two values.
  The synaptic weight takes only two values, $\pm1$.
  (\ref{fig:binary_model}) The two-state model is parameterised by the two transition probabilities.
  (\ref{fig:multistate_model}) In the multistate model the transition probabilities for potentiation/depression are all equal and it is parameterised X
  by these two values.
  The synaptic weight varies linearly in the interval $[-1,1]$.
  (\ref{fig:cascade_model}) In the cascade model, the transition probabilities decay geometrically with a parameter $x$ (see \cite{Fusi2005cascade}) and synaptic weight takes only two values.
  } \label{fig:models}
\end{figure}

@@

\begin{figure}[p]
 \begin{center}
  \aligntop{\includegraphics[height=4cm]{pooled.svg}}
 \end{center}
  \caption[The pooled resource model]{The pooled resource model.
  Several two-state synapses share resources that are required for potentiation and depression.
  These resources are depleted as more synapses are potentiated or depressed.
  This pool of synapses can be modelled as one compound synapse.} \label{fig:pooled_model}
\end{figure}

@@

\begin{figure}[p]
 \begin{center}
  \aligntop{\includegraphics[height=3cm]{multistate_nonuni.svg}}
 \end{center}
  \caption[The non-uniform multistate model]{The non-uniform multistate model.
  Similar to the multistate model, \autoref{fig:models}\ref{fig:multistate_model}), the synaptic weight varies linearly in the interval $[-1,1]$, but the transition probabilities between adjacent states decays exponentially away from the central transition for both potentiation and depression.} \label{fig:nonuni_model}
\end{figure}

@@

For the most part, we set $f\dep\norm=\half$, $f\dep\inc=f\dep\norm+\Delta f$ and $f\dep\dec=f\dep\norm-\Delta f$, with $\Delta f>0$.
We use the same values for wild-type and \KO\ models for the reasons discussed above.
We will mostly treat gain-increase and decrease symmetrically, but this is not necessary.
We could adjust $r$ to keep $r\pot$ unchanged, if so desired, but this would only change the overall timescale and would not affect any of the qualitative comparisons that we are concerned with here.
The values of these parameters are listed in \autoref{tab:params}.

@@

\begin{figure}[p]
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[width=7cm]{multistate_betastar.eps}}\label{fig:multistate_betastar}
  \item\aligntop{\includegraphics[width=7cm]{multistate_deltafstar.eps}}\label{fig:multistate_deltafstar}
 \end{myenuma}
 \end{center}
  \caption[The functions $\beta^*(M)$ and $\Delta f^*(\beta,M)$]{The functions (\ref{fig:multistate_betastar}) $\beta^*(M)$, which describes when the \KO\ models have impaired learning, and (\ref{fig:multistate_deltafstar}) $\Delta f^*(\beta,M)$ for $M=10$, which describes when pre-training enhances learning.}\label{fig:multistate_star}
\end{figure}

@@

However, to avoid confusion, we found parameter values performed reasonably in these other two comparisons two for the three models that could reproduce the correct qualitative results of the four important comparisons: the \hyperref[sec:multistate]{serial model}, the \hyperref[sec:cascade]{cascade model} and the \hyperref[sec:nonuni]{non-uniform multistate model}. The learning curves are shown in \autoref{fig:fit} and the parameters are listed in \autoref{fig:fit}\ref{tab:fit}.

@@

\begin{figure}[p]
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[width=4.5cm]{serial_fit_learnS.eps}}\label{fig:serial_fit}
  \item\aligntop{\includegraphics[width=4.5cm]{cascade_fit_learnS.eps}}\label{fig:cascade_fit}
  \item\aligntop{\includegraphics[width=4.5cm]{nonuni_fit_learnS.eps}}\label{fig:nonuni_fit}

>>>>

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
\documentclass[10pt]{article}
%\usepackage[printfigures]{figcaps}
%\usepackage[nolists,nomarkers]{endfloat}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
\hypersetup{colorlinks,linkcolor=blue,citecolor=teal,urlcolor=teal}
\input{sl_graphics_preamble.tex}
\graphicspath{{"Figures/"}}
%
\usepackage{array}
\newcounter{tablerow}[table]
\newcommand{\tablerowautorefname}{row}
\newenvironment{tabularn}[1]{\begin{tabular}{#1>{\refstepcounter{tablerow}}l}}{\end{tabular}}
%\usepackage{etoolbox}
%\AtBeginEnvironment{tabular}{\setcounter{tablerow}{0}}
\renewcommand{\figureautorefname}{Supplementary Figure}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\I}{\mathbf{I}}
%vec of ones
%equilibrium distribution
\newcommand{\pr}{\mathbf{p}}
\newcommand{\eq}{\pr^\infty}
%other symbols
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\frg}{\W^\mathrm{F}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\F}{\boldsymbol{\Phi}}
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
\newcommand{\norm}{_0}
\newcommand{\inc}{_{\text{inc}}}
\newcommand{\dec}{_{\text{dec}}}
\newcommand{\incdec}{_{\text{inc/dec}}}
\newcommand{\wt}{_{\text{WT}}}
%\newcommand{\ko}{_{\text{D$^\mathrm{b}$K$^\mathrm{b}$-/-}}}
\newcommand{\KO}{D$^\mathrm{b}$K$^{\mathrm{b}-/-}$}
\newcommand{\ko}{_{\text{MHC}}}
%\newcommand{\KO}{MHC}
\newcommand{\tpre}{t_{\text{pre}}}
\newcommand{\ttrain}{t_{\text{train}}}
\newcommand{\lmax}{_{\text{max}}}
\newcommand{\lmin}{_{\text{min}}}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{Understanding both enhanced and impaired learning with enhanced plasticity: a saturation hypothesis (supplementary material)}
%
%% Author List:
%%
%\author{An Author$^a$, Another Author$^b$ and Yet Another Author$^c$\\
%%
%\small{\emph{$^a$ Address 1}}\\
%\small{\emph{$^b$ Address 2}}\\
%\small{\emph{$^c$ Address 3}}\\
%}
\date{}
\DeclareCaptionLabelFormat{supp}{\textbf{#1 S#2}}
\captionsetup{labelformat=supp}

@@

\setcounter{page}{5}
\setcounter{figure}{4}
\maketitle

@@

\begin{figure}
 \begin{center}
 \parbox{0.8\linewidth}{%
 \begin{myenuma}
  \item\aligntop{\includegraphics[height=1.7cm]{serial.svg}}\label{fig:serial_model}\hspace{0.5cm}
  \item\aligntop{\includegraphics[height=1.7cm]{binary.svg}}\label{fig:binary_model}\hspace{0.5cm}\\[1cm]
  \item\aligntop{\includegraphics[height=1.7cm]{multistate.svg}}\label{fig:multistate_model}\hspace{0.5cm}
  \item\aligntop{\includegraphics[height=2.5cm]{cascade.svg}}\label{fig:cascade_model}
 \end{myenuma}
 }
 \end{center}
  \caption[Transition probabilities for different models]{Transition probabilities for different models.
  Potentiation induces transitions indicated by orange arrows, depression indicated by blue arrows.
  States of strong/weak synaptic weight indicated by orange/blue circles.
  (\ref{fig:serial_model}) In the serial model the transition probabilities for potentiation/depression are all equal and it is parameterised by these two values.
  The synaptic weight takes only two values, $\pm1$.
  (\ref{fig:binary_model}) The two-state model is parameterised by the two transition probabilities.
  (\ref{fig:multistate_model}) In the multistate model the transition probabilities for potentiation/depression are all equal and it is parameterised  by these two values.
  The synaptic weight varies linearly in the interval $[-1,1]$.
  (\ref{fig:cascade_model}) In the cascade model, the transition probabilities decay geometrically with a parameter $x$ (see \cite{Fusi2005cascade}) and synaptic weight takes only two values.
  } \label{fig:models}
\end{figure}

@@

\begin{figure}
 \begin{center}
  \aligntop{\includegraphics[height=4cm]{pooled.svg}}
 \end{center}
  \caption[The pooled resource model]{The pooled resource model.
  Several two-state synapses share resources that are required for potentiation and depression.
  These resources are depleted as more synapses are potentiated or depressed.
  This pool of synapses can be modelled as one compound synapse.} \label{fig:pooled_model}
\end{figure}

@@

\begin{figure}
 \begin{center}
  \aligntop{\includegraphics[height=3cm]{multistate_nonuni.svg}}
 \end{center}
  \caption[The non-uniform multistate model]{The non-uniform multistate model.
  Similar to the multistate model, (\autoref{fig:models}\ref{fig:multistate_model}), the synaptic weight varies linearly in the interval $[-1,1]$, but the transition probabilities between adjacent states decays exponentially away from the central transition for both potentiation and depression.} \label{fig:nonuni_model}
\end{figure}

@@

For the most part, we set $f\dep\norm=\half$, $f\dep\inc=f\dep\norm+\Delta f$ and $f\dep\dec=f\dep\norm-\Delta f$, with $\Delta f>0$.
We use the same values for wild-type and \KO\ models for the reasons discussed above.
We will mostly treat gain-increase and decrease symmetrically, but this is not necessary.
We could adjust $r$ to keep $r\pot$ unchanged, if so desired, but this would only change the overall timescale and would not affect any of the qualitative comparisons that we are concerned with here.
The values of these parameters are listed in \autoref{fig:sim_results}\ref{tab:params}.

@@

\begin{figure}
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[width=0.45\linewidth]{multistate_betastar.eps}}\label{fig:multistate_betastar}
  \item\aligntop{\includegraphics[width=0.45\linewidth]{multistate_deltafstar.eps}}\label{fig:multistate_deltafstar}
 \end{myenuma}
 \end{center}
  \caption[The functions $\beta^*(M)$ and $\Delta f^*(\beta,M)$]{The functions (\ref{fig:multistate_betastar}) $\beta^*(M)$, which describes when the \KO\ models have impaired learning, and (\ref{fig:multistate_deltafstar}) $\Delta f^*(\beta,M)$ for $M=10$, which describes when pre-training enhances learning.}\label{fig:multistate_star}
\end{figure}

@@

However, to avoid confusion, we found parameter values performed reasonably in these other two comparisons for the three models that could reproduce the correct qualitative results of the four important comparisons: the \hyperref[sec:multistate]{serial model}, the \hyperref[sec:cascade]{cascade model} and the \hyperref[sec:nonuni]{non-uniform multistate model}. The learning curves are shown in \autoref{fig:fit} and the parameters are listed in \autoref{fig:fit}\ref{tab:fit}.

@@

\begin{figure}
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[width=0.28\linewidth]{serial_fit_learnS.eps}}\label{fig:serial_fit}
  \item\aligntop{\includegraphics[width=0.28\linewidth]{cascade_fit_learnS.eps}}\label{fig:cascade_fit}
  \item\aligntop{\includegraphics[width=0.28\linewidth]{nonuni_fit_learnS.eps}}\label{fig:nonuni_fit}
